The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-21 project/paper/intro.tex
Changed footnote intro.

One of the most basic distributions in statistics is the binomial, $X \sim
Bin(n,p)$, $n = 0, 1, 2 \ldots$, $p \in (0, 1)$ with probability density
function (pdf)

@@

\footnotetext{A random variable $X$ follows the normal distribution with mean
$\mu$ and variance $\sigma^2$ if it has the pdf

\begin{equation*}
  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
\end{equation*}

for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\

$N(0,1)$ is an important special case known as the standard normal (denoted
$Z$) and has pdf

\begin{equation*}
  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
\end{equation*}

and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\

Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}

>>>>

One of the most basic distributions in statistics is the binomial, $X \sim
Bin(n,p)$, $n \in \N$\footnote{That is, integers greater than 0.}, $p \in (0,
1)$ with probability density function (pdf)

@@

\footnotetext{A random variable $X$ follows the normal distribution with mean
$\mu$ and variance $\sigma^2$ (denoted $X \sim N(\mu,\sigma^2)$) if it has the
pdf $f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \;
e^{-[(x-\mu)/\sigma]^2/2}$ for $-\infty < x < \infty$, where $-\infty < \mu <
\infty$ and $0 < \sigma < \infty$.

$N(0,1)$ is an important special case known as the standard normal (denoted
$Z$) and has pdf $\phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty
< z < \infty$ and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.
Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}

### 2011-01-21 project/paper/output.tex
Changed footnote intro.

\footnotetext{A random variable $X$ follows the normal distribution with mean
$\mu$ and variance $\sigma^2$ if it has the pdf

\begin{equation*}
  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
\end{equation*}

for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\

$N(0,1)$ is an important special case known as the standard normal (denoted
$Z$) and has pdf

\begin{equation*}
  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
\end{equation*}

and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\

Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}

>>>>

\footnotetext{A random variable $X$ follows the normal distribution with mean
$\mu$ and variance $\sigma^2$ (denoted $X \sim N(\mu,\sigma^2)$) if it has the
pdf $f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \;
e^{-[(x-\mu)/\sigma]^2/2}$ for $-\infty < x < \infty$, where $-\infty < \mu <
\infty$ and $0 < \sigma < \infty$.

$N(0,1)$ is an important special case known as the standard normal (denoted
$Z$) and has pdf $\phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty
< z < \infty$ and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.
Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}

%\footnotetext{A random variable $X$ follows the normal distribution with mean
%$\mu$ and variance $\sigma^2$ if it has the pdf
%
%\begin{equation*}
%  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
%\end{equation*}
%
%for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
%\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
%
%$N(0,1)$ is an important special case known as the standard normal (denoted
%$Z$) and has pdf
%
%\begin{equation*}
%  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
%\end{equation*}
%
%and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
%
%Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
